The Bug Catalog of the Maven Ecosystem

### 2014-01-20 docs/msr.tex
added related work section draft

Cite~\cite{RDV13}.

>>>>

The Maven ecosystem has been previously analyzed by
Raemaekers et al.~\cite{RDV13}
to produce the {\it Maven dependency dataset}.
Apart from basic information like individual methods, classes,
packages and lines of code for every {\sc jar}, the dataset
also includes a database with all the
connections between the aforementioned elements.
